---
title: "R Notebook"
output: html_notebook
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(data.table))
rm(list=ls())
library(dplyr)
#install.packages("devtools")
library(devtools)
#install_github("easyGgplot2", "kassambara")
#install_github("kassambara/easyGgplot2")
library(easyGgplot2)
```

```{r , echo = FALSE}
setwd('C:/Users/pro/Desktop')
hcmv = fread("hcmv.txt")
hcmv <- hcmv[!hcmv$location == 'NA',]
```

Q1
```{r}
N <- 229354
n <- 296
set.seed(296)
gene <- seq(1, N)
site.random <- sample.int(N, size=n)
library(lattice)
stripplot(site.random, pch=16, cex=0.25)

hcmv <- fread("hcmv.txt")
hcmv <- hcmv[-297,]
hist(site.random,  col = rgb(1,0,0,0.5), xlab = "site", main = "Histogram of Simulated Data and Observed Data",probability = TRUE,ylim=c(0,8e-06))
lines(density(site.random,adjust=2), col = rgb(1,0,0,0.5))
hist(hcmv$location,  col = rgb(0,0,1,0.5),  add = TRUE,probability = TRUE)
lines(density(hcmv$location,adjust=2), col = rgb(0,0,1,0.5))
legend(x = 175000, y = 8e-06, legend = c("simulated", "observed"), lty = c(1,1), col = c(rgb(1,0,0,0.5), rgb(0,0,1,0.5)))
```

Q2
```{r}
#Question 2 
n <- 296
#create a new dataframe for consecutive palindromes
x1 <- hcmv[1:295,c(1)]
x2 <- hcmv[2:296,c(1)]
consecutive <- (x2 - x1)
con_df <- data.frame(x1,x2,consecutive)
names(con_df) <- c("x1","x2","consecutive")
first_obs <- data.frame(0,177,0)
names(first_obs) <- c("x1","x2","consecutive")
con_new <- rbind(first_obs,con_df) 
#make a scatter plot
sca_x <- con_new$x2
sca_y <- con_new$consecutive
plot(sca_x,sca_y, main = "Spaces between Consecutive Palindromes",
    xlab = "296 Palindromes",ylab = "Numbers of spaces(as DNA base pairs)",
    pch = 18, frame = TRUE)
abline(lm(sca_y~sca_x,data = con_new),col = "blue")

# make a histogram of consecutive palindromes spacing

# create a new dataframe for consecutive pairs
x2_1 <- hcmv[1:294,c(1)]
x2_2 <- hcmv[3:296,c(1)]
consecutive2 <- (x2_2 - x2_1)
con2_df <- data.frame(x2_1,x2_2,consecutive2)

names(con2_df) <- c("x2_1","x2_2","consecutive2")


plot(con2_df$x2_2,con2_df$consecutive2, main = "Spaces between Consecutive Palindrome Pairs",
     xlab = "296 Palindromes",ylab = "Numbers of spaces(as DNA base pairs)",
     pch = 18, frame = TRUE,col = "grey")
abline(lm(sca_y~sca_x,data = con_new),col = "blue")

# create a new dataframe for consecutive triplets
x3_1 <- hcmv[1:293,c(1)]
x3_2 <- hcmv[4:296,c(1)]
consecutive3 <- (x3_2 - x3_1)
con3_df <- data.frame(x3_1,x3_2,consecutive3)

names(con3_df) <- c("x3_1","x3_2","consecutive3")

plot(con3_df$x3_2,con3_df$consecutive3, main = "Spaces between Consecutive Palindrome Triplets",
     xlab = "296 Palindromes",ylab = "Numbers of spaces(as DNA base pairs)",
     pch = 18, frame = TRUE,col = "Pink")
abline(lm(sca_y~sca_x,data = con_new),col = "blue")

#Histogram of 3 different type of spaces
single <- rep("single spacing", 295)
pair <- rep("pair spacing",294)
triplet <- rep("triplet spacing",293)
compare1 <- data.frame(single,consecutive)
compare2 <- data.frame(pair,consecutive2)
compare3 <- data.frame(triplet,consecutive3)
names(compare1) <- c("type","space")
names(compare2) <- c("type","space")
names(compare3) <- c("type","space")
compare <- rbind(compare1,compare2,compare3)
ggplot2.histogram(data=compare, xName="space",
                  groupName="type", legendPosition="right",
                  alpha=0.4, addDensity=TRUE,
                  addMeanLine=TRUE, meanLineColor="white", meanLineSize=1)

ggplot2.histogram(data=compare, xName="space",
                  groupName="type", legendPosition="right",
                  alpha=0.4, addDensity=FALSE,
                  addMeanLine=FALSE, meanLineColor="white", meanLineSize=1)

```

Q3
```{r}
#Find the right interval length
r = 2*296^(2/5)
r
#Choose smaller ones
#Observe that if we take r = 23, can still achieve n*p >= 5
observedTable = table(cut(hcmv$location,breaks = c(10000*0:23)))#all elements greater than 5.
observed = as.vector(observedTable)

#Compare graphically using histogram
par(mfrow=c(1,2))
hist(hcmv$location, breaks = c(10000*0:23), freq = TRUE, labels = TRUE, col = "lightblue", main = "Frequency of locations 1", xlab = "Observed locations", ylim = c(0, 25), xlim = c(0, 250000))
hist(site.random, breaks = c(10000*0:23), main = "Frequency of locations 2", freq = TRUE, labels = TRUE, col = "lightpink", ylim = c(0,25), xlim = c(0, 250000), xlab = "random locations")
#Observation: mean = 296/23 = 12.8696. 60000-80000 much higher, 80000-90000 much lower, 90000-100000 much higher, 190000-200000 much higher, 200000-220000 much lower, 220000-230000 much higher. Both have two extreme high intervals. Compare with uniform: more extremes
```

Q3 Part 2
```{r}
#Compare with poisson distribution graphically
#generate a poisson distribution
poissonGenerated = rpois(296, lambda = mean(observed))
#compare graphically
hist(poissonGenerated, breaks = 23, probability = TRUE, col = rgb(1,0,0,0.4), main = "Number of counts", ylim = c(0,0.25), xlim = c(3,25), xlab = "Counts")
lines(density(poissonGenerated, adjust = 2), col = "darkgreen", lty = 2)
hist(observed, breaks = 23, col = rgb(0,0,1,0.4), probability = TRUE, add = TRUE)
lines(density(observed, adjust = 2), col = "darkblue")
legend(x = 20, y = 0.25, legend = c("poisson", "observed"), lty = c(2, 1), col = c("darkgreen", "darkblue"))

#Compare with generated distribution rigorously using chi-squared test
#With randomly generated sample
generatedTable = table(cut(site.random,breaks = c(10000*0:23)))
generated = as.vector(generatedTable)
p.generated = generated/296
chisq.test(observed, p = p.generated)#Rej
#With poisson distributed sample
poissonedTable = table(cut(poissonGenerated, breaks = 23))
poiss = as.vector(poissonedTable)
chisq.test(observed, poiss)#Fail

#Sensitivity for overall shape
#Compare with randomly generated sample
#Decrease interval
observed.decTable = table(cut(hcmv$location,breaks = c(9557*0:24)))#all elements greater than 5.
generated.decTable = table(cut(site.random,breaks = c(9557*0:24)))
observed.dec = as.vector(observed.decTable)
generated.dec = as.vector(generated.decTable)
p.generated.dec = generated.dec/296
chisq.test(observed.dec, p = p.generated.dec)#Rej

#Increase interval
observed.incTable = table(cut(hcmv$location,breaks = c(10426*0:22)))#all elements greater than 5.
generated.incTable = table(cut(site.random,breaks = c(10426*0:22)))
observed.inc = as.vector(observed.incTable)
generated.inc = as.vector(generated.incTable)
p.generated.inc = generated.inc/296
chisq.test(observed.inc, p = p.generated.inc)#Rej

#Compare with poison generated sample
#Decrease interval
poissonedTable.dec = table(cut(poissonGenerated, breaks = 24))
poiss.dec = as.vector(poissonedTable.dec)
chisq.test(observed.dec,poiss.dec)#Fail

#Increase interval
poissonedTable.inc = table(cut(poissonGenerated, breaks = 22))
poiss.inc = as.vector(poissonedTable.inc)
chisq.test(observed.inc,poiss.inc)#Fail

#Classify regions
#Classify according to their differences
observed1Table = table(cut(hcmv$location,breaks = c(2000*1:116)))
generated1Table = table(cut(site.random,breaks = c(2000*1:116)))
observed1 = as.vector(observed1Table)
generated1 = as.vector(generated1Table)
diff = abs(observed1 - generated1)
hist(diff, main = "Diffrences between observed and randomly generated values", xlab = "Differences", col = "darkblue", ylim = c(0,60), xlim = c(0, 11), labels = TRUE)
classifying.value1 = mean(diff) + 2*sqrt(var(diff))
classifying.value2 = mean(diff) + 1*sqrt(var(diff))
classifying.value1#5.238282
classifying.value2#3.575663
```

Q4
```{r}
#Compare rigorously using proportional test(use smaller interval)
hist(hcmv$location, breaks = c(2000*0:116), freq = TRUE, labels = TRUE, col = "lightblue", main = "Frequency of locations with interval length 2000", xlab = "locations")
hist(site.random, breaks = c(2000*0:116), freq = TRUE, labels = TRUE, col = "lightpink", main = "Random scattered frequency of locations with interval length 2000", xlab = "locations")
#cannot perform chi-squared test since some bins have less than 5 elements. Use proportional test to examine exceptional bins
#92000-94000(2000)
prop.test(c(12,1), c(296,296), alternative = c("greater"))#Rej
#194000-196000(2000)
prop.test(c(8,4), c(296,296), alternative = c("greater"))#Fail
#Sensitivity for exceptional bins
#Increase interval
observed1.inc = table(cut(hcmv$location,breaks = c(2100*1:110)))
generated1.inc = table(cut(site.random,breaks = c(2100*1:110)))
#13,2(93000),9,3(195000)
prop.test(c(13,2), c(296,296), alternative = c("greater"))#Rej
prop.test(c(9,3), c(296,296), alternative = c("greater"))#Fail
#Decrease interval
observed1.dec = table(cut(hcmv$location,breaks = c(1900*1:121)))
generated1.dec = table(cut(site.random,breaks = c(1900*1:121)))
#11,2(93000),8, 3(195000)
prop.test(c(11,2), c(296,296), alternative = c("greater"))#Rej
prop.test(c(8,3), c(296,296), alternative = c("greater"))#Fail

#use simulation test to check if the cluster would appear in random generations
N <- 229354
n <- 296
simulated = 0
times = 0:999
simulated.max <- c()
for (i in times){
  random <- sample.int(N, size=n)
  random.generated <- table(cut(random,breaks = c(2000*1:112)))
  observed <- table(cut(hcmv$location,breaks = c(2000*1:112)))
  #check if the big cluster would exist in random generations
  if (max(observed) <= max(random.generated)){
    simulated <- simulated + 1
  }
  simulated.max <- c(simulated.max, max(random.generated))
}
#the chance that clusters appear in random generations
p.value.2000 = simulated/1000
#graph the maximum counts in 1000 simulated DNA
hist(simulated.max, 
     main = "Max Counts with Cut Size 2000",
     xlab="Max Counts",
     col="#009999")

#we should also check for other ways of cutting the DNA, we take half the size for each piece
for (i in times){
  random <- sample.int(N, size=n)
  random.generated <- table(cut(random,breaks = c(1000*1:230)))
  observed <- table(cut(hcmv$location,breaks = c(1000*1:230)))
  #check if the big cluster would exist in random generations
  if (max(observed) <= max(random.generated)){
    simulated <- simulated + 1
  }
  simulated.max <- c(simulated.max, max(random.generated))
}
#the chance that clusters appear in random generations
p.value.1000 = simulated/1000
#graph the maximum counts in 1000 simulated DNA
hist(simulated.max, 
     main = "Max Counts with Cut Size 1000",
     xlab="Max Counts",
     col="#996633")

#we should also check for other ways of cutting the DNA, we half the size for each piece again
for (i in times){
  random <- sample.int(N, size=n)
  random.generated <- table(cut(random,breaks = c(500*1:460)))
  observed <- table(cut(hcmv$location,breaks = c(500*1:460)))
  #check if the big cluster would exist in random generations
  if (max(observed) <= max(random.generated)){
    simulated <- simulated + 1
  }
  simulated.max <- c(simulated.max, max(random.generated))
}
#the chance that clusters appear in random generations
p.value.500 = simulated/1000
#graph the maximum counts in 1000 simulated DNA
hist(simulated.max, 
     main = "Max Counts with Cut Size 500",
     xlab="Max Counts",
     col="darkmagenta")
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
?hist
