---
title: "Math189_Project2_final_code"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(data.table))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(dplyr))
library(e1071)

# setwd('/mnt/genomics/Kysha/ImmunoCancer/Yibei/189')
```

#import data
```{r video}
video_dt <- fread("video.txt")
videoMultiple = fread("videoMultiple.txt")
colnames(videoMultiple)
names(videoMultiple)[6] = "relax"
names(videoMultiple)[7] = "coord"
names(videoMultiple)[8] = "challenge"
names(videoMultiple)[9] = "master"
names(videoMultiple)[10] = "bored"
names(videoMultiple)[11] = "other"
names(videoMultiple)[12] = "graphic"
names(videoMultiple)[13] = "time"
names(videoMultiple)[14] = "frust"
names(videoMultiple)[15] = "lonely"
names(videoMultiple)[16] = "rules"
names(videoMultiple)[17] = "cost"
names(videoMultiple)[18] = "boring"
names(videoMultiple)[19] = "friends"
names(videoMultiple)[20] = "point"
names(videoMultiple)[21] = "other2"

```

############Scenario 1
```{r}
#calculate population proportion of students who played video games in the week prior to the exam
video_s1 <- video_dt
time_col <- video_s1$time
pop_size <- 3000
sample_size <- nrow(video_s1)
played_num <- nrow(video_s1[!video_s1$time == 0,])
sample_prop <- played_num/sample_size
standard_error <- qnorm(0.975) * sqrt(sample_prop*(1-sample_prop))/sqrt(sample_size-1)*(sqrt(pop_size-sample_size)/sqrt(pop_size))
left <- sample_prop - standard_error
right <- sample_prop + standard_error
```


############Scenario 2
```{r plot}
#clean up the outliers in freq
video_s2 <- video_dt[video_dt$freq != 99]
video_s2<-video_s2[video_s2$time != 30]

```

```{r plot}
par(mfrow = c(1,2))
hist(video_s2$freq, breaks=c(0,1,2,3,4),main = paste("Histogram of" , "frequency of played"),xlab="frequency of play")
hist(video_s2$time, breaks=seq(0,14,l=15), main = paste("Histogram of" , "time"),xlab="time")
```

```{r plot}
video_1 <- video_s2[video_s2$time ==0]
video_2 <- video_s2[video_s2$time !=0]
par(mfrow = c(1,3))
hist(video_1$freq, breaks=c(0,1,2,3,4),main = "frequency of played for time zero",xlab="frequency of play")
hist(video_2$freq, breaks=c(0,1,2,3,4),main = "frequency of played for non-zero time",xlab="frequency of play")
hist(video_2$time,, breaks=seq(0,14,l=15), main = "time played for non-zero time",xlab="frequency of play")
```

```{r boxplot}
video_1f <- video_s2[video_s2[["freq"]]==1]
video_2f <- video_s2[video_s2[["freq"]]==2]
video_3f <- video_s2[video_s2[["freq"]]==3]
video_4f <- video_s2[video_s2[["freq"]]==4]
video_1f$time <- video_1f$time/7
video_3f$time <- video_3f$time*4
video_4f$time <- video_4f$time*15
boxplot(video_1f$time,video_2f$time,video_3f$time, video_4f$time,
        main = "Time played for different people play with different frequency",
        names = c("daily","weekly", "monthly","semesterly"),
        las = 2,
        xlab = 'time played',
        col = c('red','blue','green','orange'),
        border = 'black',
        horizontal = TRUE)
```

############Scenario 3
```{r}
##plor histogram
video_s3 <- video_dt
# Add a Normal Curve to the histogram (sample distribution)
x <- video_s3$time
h<-hist(x, breaks=12, col="blue", xlab="# of hours played in the week",
           main="Histogram with Normal Curve of Hours Played in the Week")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x)
lines(xfit, yfit, col="orange", lwd=2)
```

#perform one sample t test
```{r}
t.test(video_s3$time)

#One Sample t-test

#data:  video_s3$time
#t = 3.139, df = 90, p-value = 0.002293
#alternative hypothesis: true mean is not equal to 0
#95 percent confidence interval:
#  0.4562505 2.0294638
#sample estimates:
#  mean of x 
#1.242857

kurtosis(video_s3$time)
```




#bootstrape
```{r}
bootobject = NULL
for (i in 1:500) {
  bootobject[i] = mean(sample(as.vector(video_s3$time),size = 55,replace =TRUE))
}

m = qplot(bootobject,geom = "histogram",xlab = "bootobject",main = "Bootstrap-average amount of time played/wk")
m + geom_histogram(aes(fill = ..count..))
kurtosis(bootobject)
skewness(bootobject)
a = qqnorm(bootobject, main = "QQplot of Bootstrapped samples")
```

```{r}
require(e1071)
#kurtosis
kurtosis_=NULL
for(i in 1:1000){
  kurtosis_[i]=kurtosis(rnorm(500))
}
mean(kurtosis_) #-0.01900885-0.01900885
m = qplot(kurtosis_,geom="histogram",main = "Simulated Distribution of Kurtosis")
m + geom_histogram(aes(fill = ..count..))

#Skewness
skewness_=NULL
for(i in 1:1000){
  skewness_[i]=kurtosis(rnorm(500))
}
mean(skewness_) # one round :-0.02773595
m = qplot(skewness_,geom="histogram",main = "Simulated Distribution of Skewness")
m + geom_histogram(aes(fill = ..count..))

# the final result for s3
t.test(bootobject)$"conf.int"
```

#jackknife
```{r}
jackobject = NULL
for (i in 1:500) {
  jackobject[i] = mean(sample(as.vector(video_s3$time),size = 90,replace =TRUE))
}

m = qplot(jackobject,geom = "histogram",xlab = "jackknife object",main = "jackknife - average amount of time played/wk")
m + geom_histogram(aes(fill = ..count..))

kurtosis(jackobject)
skewness(jackobject)
```

############Scenario 4
```{r, include = FALSE}
#Data cleaningã€
video_s4 <- video_dt
video_s4 <- video_s4[!video_s4$like == '99',]
video_s4.Played = video_s4[video_s4$like != '1' ,]
videoMultiple <- videoMultiple[!videoMultiple$relax == "NA",]
#Like or not(out of 89)
veryLike = video_s4[video_s4$like == '2',]#23
somewhatLike = video_s4[video_s4$like == '3',]#46
notreallyLike = video_s4[video_s4$like == '4',]#13
dontLike = video_s4[video_s4$like == '5',]#7
#prop.test
prop.test(69, 89,p = 0.5, alternative = c("greater"), conf.level = 0.99)
#Reason for like(out of 87)
relax = videoMultiple[videoMultiple$relax == '1' ,]#58
coordination = videoMultiple[videoMultiple$coord == '1' ,]#4
challenge = videoMultiple[videoMultiple$challenge == '1' ,]#21
master = videoMultiple[videoMultiple$master == '1' ,]#25
bored = videoMultiple[videoMultiple$bored == '1' ,]#24
graphic = videoMultiple[videoMultiple$graphic == '1' ,]#23
#prop.test
prop.test(58, 87,p = 0.5, alternative = c("greater"), conf.level = 0.99)
#Reason for dislike(out of 87)
time = videoMultiple[videoMultiple$time == '1' ,]#42
frustrating = videoMultiple[videoMultiple$frust == '1' ,]#23
lonely = videoMultiple[videoMultiple$lonely == '1' ,]#4
rules = videoMultiple[videoMultiple$rules == '1' ,]#17
cost = videoMultiple[videoMultiple$cost == '1' ,]#35
boring = videoMultiple[videoMultiple$boring == '1' ,]#14
noFriend = videoMultiple[videoMultiple$friends == '1' ,]#2
pointless = videoMultiple[videoMultiple$point == '1' ,]#29
```

############Scenario 5
```{r, include = FALSE}
video_s5 <- video_dt
#data cleaning
video_s5 <- video_s5[!video_s5$like == '99',]
video_s5 <- video_s5[!video_s5$educ == '99',]
video_s5.Played = video_s5[video_s5$like != '1' ,]
#Table visualization
sex.Freq = table(video_s5.Played$like, video_s5.Played$sex)
sex.Freq
#Combine rows
X = as.table(rbind(c(26, 42), c(12, 8)))
dimnames(X) = list(attitude = c("Like", "Dislike"), gender = c("f", "M"))
X
#prop.test
prop.test(c(26,42), c(38,50))
#Table visualization
own.Freq = table(video_s5.Played$like, video_s5.Played$own)
own.Freq
#Combine rows
X = as.table(rbind(c(21, 47), c(3, 17)))
dimnames(X) = list(attitude = c("Like", "Dislike"), own = c("NO", "YES"))
X
#prop.test
prop.test(c(21,47),c(24,64))
#Table visualization
educ.Freq = table(video_s5.Played$like, video_s5.Played$educ)
educ.Freq
#Combine rows
X = as.table(rbind(c(30, 35), c(10, 2)))
dimnames(X) = list(attitude = c("Like", "Dislike"), educ = c("NO", "YES"))
X
#prop.test
prop.test(c(30,35),c(40,37))
```

############Scenario 6

```{r data, include = FALSE}
games6 <- video_dt
gamesMultiple = fread("videoMultiple.txt")
gamesMultiple
colnames(gamesMultiple)
names(gamesMultiple)[1] <- "action"
names(gamesMultiple)[2] <- "adv"
names(gamesMultiple)[3] <- "sim"
names(gamesMultiple)[4] <- "sport"
names(gamesMultiple)[5] <- "strategy"
gamesMultiple

library(dplyr)
grade = select(games6, grade)
type = select(gamesMultiple, c('action', 'adv','sim','sport','strategy'))
gamesNew = mutate(type, grade)

games.type = na.omit(gamesNew)
games.type = games.type[!games.type$action == '99',]
games.type = games.type[!games.type$adv == '99',]
games.type = games.type[!games.type$sim == '99',]
games.type = games.type[!games.type$sport == '99',]
games.type = games.type[!games.type$strategy == '99',]
games.type = games.type[!games.type$grade == '99',]
```

connecting grade expectation with video games preference (whether the students like playing game or not)

```{r like, echo = FALSE}
games.like = na.omit(games6)
games.like = games.like[!games.like$like == '99',]
never = games.like[games.like$like == '1',]
very = games.like[games.like$like == '2',]
somewhat = games.like[games.like$like == '3',]
notreally = games.like[games.like$like == '4',]
no = games.like[games.like$like == '5',]


library(moments)

mean(never$grade)
sd(never$grade)
skewness(never$grade)
kurtosis(never$grade)

mean(very$grade)
sd(very$grade)
skewness(very$grade)
kurtosis(very$grade)

mean(somewhat$grade)
sd(somewhat$grade)
skewness(somewhat$grade)
kurtosis(somewhat$grade)

mean(notreally$grade)
sd(notreally$grade)
skewness(notreally$grade)
kurtosis(notreally$grade)

mean(no$grade)
sd(no$grade)
skewness(no$grade)
kurtosis(no$grade)

par(mfrow = c(2,3))
hist(never$grade, breaks = c(-0.5,0.5, 1.5, 2.5, 3.5, 4.5), main = "never played students", xlab = "grade expectation", labels = c("F", "D", "C", "B", "A"), ylim = c(0,30))
hist(very$grade, breaks = c(-0.5,0.5, 1.5, 2.5, 3.5, 4.5), main = "very much students", xlab = "grade expectation", labels = c("F", "D", "C", "B", "A"), ylim = c(0,30))
hist(somewhat$grade, breaks = c(-0.5,0.5, 1.5, 2.5, 3.5, 4.5), main = "somewhat students", xlab = "grade expectation", labels = c("F", "D", "C", "B", "A"), ylim = c(0,30))
hist(notreally$grade, breaks = c(-0.5,0.5, 1.5, 2.5, 3.5, 4.5), main = "not really students", xlab = "grade expectation", labels = c("F", "D", "C", "B", "A"), ylim = c(0,30))
hist(no$grade, breaks = c(-0.5,0.5, 1.5, 2.5, 3.5, 4.5), main = "not at all students", xlab = "grade expectation", labels = c("F", "D", "C", "B", "A"), ylim = c(0,30))

```

connecting grade expectation with video games preference (types of games)

```{r relation, echo = FALSE}
action = games.type[games.type$action == '1',]
adv = games.type[games.type$adv == '1',]
sim = games.type[games.type$sim == '1',]
sport = games.type[games.type$sport == '1',]
strategy = games.type[games.type$strategy == '1',]

library(moments)

mean(action$grade)
sd(action$grade)
skewness(action$grade)
kurtosis(action$grade)

mean(adv$grade)
sd(adv$grade)
skewness(adv$grade)
kurtosis(adv$grade)

mean(sim$grade)
sd(sim$grade)
skewness(sim$grade)
kurtosis(sim$grade)

mean(sport$grade)
sd(sport$grade)
skewness(sport$grade)
kurtosis(sport$grade)

mean(strategy$grade)
sd(strategy$grade)
skewness(strategy$grade)
kurtosis(strategy$grade)

par(mfrow = c(2,3))
hist(action$grade, breaks = c(-0.5, 0.5, 1.5, 2.5, 3.5, 4.5), main = "action players' grade expectations", xlab = "grade expectation", labels = c("F", "D", "C", "B", "A"), ylim = c(0,30))
hist(adv$grade, breaks = c(-0.5, 0.5, 1.5, 2.5, 3.5, 4.5), main = "adventure players' grade expectations", xlab = "grade expectation", labels = c("F", "D", "C", "B", "A"), ylim = c(0,30))
hist(sim$grade, breaks = c(-0.5, 0.5, 1.5, 2.5, 3.5, 4.5), main = "simulation players' grade expectations", xlab = "grade expectation", labels = c("F", "D", "C", "B", "A"), ylim = c(0,30))
hist(sport$grade, breaks = c(-0.5, 0.5, 1.5, 2.5, 3.5, 4.5), main = "sport players' grade expectations", xlab = "grade expectation", labels = c("F", "D", "C", "B", "A"), ylim = c(0,30))
hist(strategy$grade, breaks = c(-0.5, 0.5, 1.5, 2.5, 3.5, 4.5), main = "strategy players' grade expectations", xlab = "grade expectation", labels = c("F", "D", "C", "B", "A"), ylim = c(0,30))


```
grade expectation distribution v.s. target distribution

```{r}
A = sum(gamesNew$grade == "4")
A
A_proportion = A / 91
A_proportion

B = sum(gamesNew$grade == "3")
B
B_proportion = B / 91
B_proportion

C = sum(gamesNew$grade == "2")
C
C_proportion = C / 91
C_proportion

D = sum(gamesNew$grade == "1") + sum(gamesNew$grade == "0")
D
D_proportion = D / 91
D_proportion

A.test = prop.test(x = A, n = 91, p = 0.2, correct = FALSE, alternative = "greater")
A.test

B.test = prop.test(x = B, n = 91, p = 0.3, correct = FALSE, alternative = "greater")
B.test

C.test = prop.test(x = C, n = 91, p = 0.4, correct = FALSE, alternative = "less")
C.test

D.test = prop.test(x = C, n = 91, p = 0.1, correct = FALSE, alternative = "less")
D.test
```
If the nonrespondents were failing students, we have

```{r fail, echo = FALSE}
A = sum(gamesNew$grade == "4")
A
A_proportion = A / 95
A_proportion

B = sum(gamesNew$grade == "3")
B
B_proportion = B / 95
B_proportion

C = sum(gamesNew$grade == "2")
C
C_proportion = C / 95
C_proportion

D = 4
D
D_proportion = D / 95
D_proportion

A.test = prop.test(x = A, n = 95, p = 0.2, correct = FALSE, alternative = "greater")
A.test

B.test = prop.test(x = B, n = 95, p = 0.3, correct = FALSE, alternative = "greater")
B.test

C.test = prop.test(x = C, n = 95, p = 0.4, correct = FALSE, alternative = "less")
C.test

D.test = prop.test(x = C, n = 95, p = 0.1, correct = FALSE, alternative = "less")
D.test

```


##########additional question 
```{r}
lmod = lm(grade~., data=games6)
summary(lmod)

```
